A Kochen-Specker system has at least 21 vectors\\ {\small (extended abstract)}

### 2014-10-23 paper/main.tex
Revert " "-" -> "--""
This reverts commit b440b7a1ae94b34e7fb09bc72303b2c4ee36082e.

\begin{abstract}
    At the heart of the Conway's Free Will theorems and Kochen and Specker's
        argument against non-contextual hidden variable theories
    is the existence of a Kochen-Specker (KS) system:
    a set of points on the sphere
    that has no~$\{0,1\}$-coloring such that
    at most one of two orthogonal points are colored~$1$
    and of three pairwise orthogonal points exactly one
    is colored~$1$.
    In public lectures, Conway encouraged the search for small
    KS systems.
    At the time of writing, the smallest known
    KS system has 31 vectors.

>>>>

\begin{abstract}
    At the heart of the Conway-Kochen's
    Free Will theorems and Kochen and Specker's
        argument against non-contextual hidden variable theories
    is the existence of a Kochen-Specker (KS) system:
    a set of points on the sphere
    that has no~$\{0,1\}$-coloring such that
    at most one of two orthogonal points are colored~$1$
    and of three pairwise orthogonal points exactly one
    is colored~$1$.
    In public lectures, Conway encouraged the search for small
    KS systems.
    At the time of writing, the smallest known
    KS system has 31 vectors.
